
\section{Experiment}
\label{sec:experiment}

The data presented was collected between 4/20/13 to 4/28/13, and is composed of approximately 4.95 million successful measurements.

\subsection{Turbo-King Implementation}
\label{sec:turbo-king}

\subsubsection{Measurement Node}
We utilized the dnspython libraries to implement our Turbo-King variant. Each measurement node runs a Turbo-King server (composed of a DNS client and server) which exposes a remote procedure call service using the RPYC library. We deployed the Turbo-King server to 56 Planet Lab nodes (fig x).

\subsubsection{Central Name Server}
Our central name server is implemented using the Python twisted framework, which allowed for highly parallel and asynchronous handling of DNS queries. We deployed 2 nameservers on Amazon EC2.

\subsubsection{Controller}
Latency measurements were centrally managed from a controller running on EC2. The controller is responsible for issuing remote-procedure calls to Turbo-King servers and storing the resulting data. The controller randomly selects 2 target name servers, the first from the set of open recursive resolvers, and the second from the set of all resolvers. It then determines the 10 nearest Turbo-King servers to the first target, issues a remote procedure call to each, and stores the results in a relational database. The controller is composed of multiple threads that follow this procedure and run continuously.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End: 
