\documentclass{sig-alternate-10pt}

\usepackage{times}
\usepackage{graphics}
\usepackage{listings}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{tabularx}
\usepackage{color}
\usepackage{xspace}
\usepackage{hyperref}    % Creates hyperlinks from ref/cite
\hypersetup{pdfstartview=FitH}
\usepackage{graphicx}    % For importing graphics
\usepackage{url}         %
\usepackage{caption}

\hypersetup{%
pdftitle={Latency Measurement and Analysis of Wide Area Networks, Data Center, and Cellular Networks}, pdfauthor={Ben Zhang, Ahir Reddy}, pdfkeywords={Internet, Latency, Measurement}, bookmarksnumbered, pdfstartview={FitH}, colorlinks,
citecolor=black, filecolor=black, linkcolor=black, urlcolor=black,
breaklinks=true,}

\renewcommand{\arraystretch}{1.2} % Space out rows in tables

\newcommand{\ml}[1]{{\color{green} {\it ML: #1}}}

% No space between bibliography items:
\let\oldthebibliography=\thebibliography
  \let\endoldthebibliography=\endthebibliography
  \renewenvironment{thebibliography}[1]{%
    \begin{oldthebibliography}{#1}%
      \setlength{\parskip}{0ex}%
      \setlength{\itemsep}{0ex}%
  }%
  {%
    \end{oldthebibliography}%
  }

%\pagenumbering{arabic}  % Arabic page numbers for submission.  Remove this line to eliminate page numbers for the camera ready copy

\begin{document}

% use this command to override the default ACM copyright statement
% (e.g. for preprints). Remove for camera ready copy.
%\toappear{Submitted for review to IPSN 2012.}
% \conferenceinfo{ConfName} {Date, Location}
% \CopyrightYear{Year} 
% \crdata{978-1-4503-1227-1/12/04} 
% \clubpenalty=10000 
% \widowpenalty = 10000


% to make various LaTeX processors do the right thing with page size
\special{papersize=8.5in,11in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\setlength{\textfloatsep}{13pt plus 2pt minus 1pt}

\title{Latency Measurement and Analysis of \\ Wide Area Networks, Data Center, and Cellular Networks}

\author{
{Ben Zhang, Ahir Reddy}\\
\affaddr{University of California, Berkeley}\\
%\affaddr{}\\
\email{benzh@eecs.berkeley.edu, ahirreddy@berkeley.edu}
}

\maketitle

\begin{abstract}
% Abstract for measurement project.
Understanding the current state of Internet performance is critical to both academic research and industrial systems. Though various metrics (connectivity, available bandwidth, etc.) are important to evaluate, in this project, we focus on the latency of current Internet (as of 2013) in the Wide Area Network (WAN), Data Center (DC), and Cellular Networks.

We employed the King/Turbo-King methods proposed in the literature to measure the latency between two arbitrary hosts. The correlation of latency with geographical location will allow for identification of the gap between existing network performance and the speed-of-light limit. Such data serves as the starting point for analyzing wide area network performance. As the number of services deployed in the Cloud continues to increase, how the latencies experienced by end-users are dependent on data center performance is unknown though many research efforts have been put to optimizing DC performance. We use Google Search in our case study to understand the composition of time in typical data center queries. Our final study explored cellular networks; more specifically we evaluated AT\&T's 4G-LTE network in the Bay Area. We utilized \texttt{traceroute} to test the latency of the new flat IP architecture in LTE networks.

\end{abstract}

%\category{C.2.1}{Computer-Communication Networks}{Network Architecture and Design}[Wireless communication]
%\keywords{Collection, CTP, Sensor Network, Routing}

% \category{B.0}{Hardware}{General}
% \category{B.4}{Hardware}{Input/Output \& Data Communication} 
% \category{H.4.m}{Information Systems Applications}{Miscellaneous}

% \terms{Design, Experimentation, Measurement} 
\keywords{Internet Latency, Measurement Study, King, Turbo King, Planet Lab, traceroute}

\input{intro.tex}
\input{related.tex}
%\input{expected_results.tex}
\input{WAN.tex}
\input{DC.tex}
\input{mobile.tex}
\input{discussion.tex}
\input{conclusion.tex}

% \section{Acknowledgments}

\bibliographystyle{abbrv}
\bibliography{Measurement}

\end{document}